---
title: "vadim"
date: "2024-05-24"
output:
  html_document:
     keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Code and simulated data for the manuscript **Influence of mRNA Covid-19 vaccine dosing interval on the risk of myocarditis** by Le Vu et al.

```{r}
knitr::read_chunk("functions.R")
```

```{r libs, warning = FALSE, message = FALSE}

```

```{r parms}

```

- We are analyzing a matched case-control study with essentially two covariates, first $V$ the recent exposure to a vaccine dose (binary variable), and $X$ a continuous time interval that represents spacing between previous and current dose.
    - While the recent exposure is a risk factor in itself, we state that the time interval only acts as a risk factor conditional on recent exposure.
    - The hypothesis for the research question is that shorter spacing between doses increase the risk of being a case in people recently vaccinated (i.e. exposed).
    - We will quantify the relation by either categorizing $X$ or modelling it continuously.
 
## Data   
- We start by simulating data from a matched case-control study. Parameters are set so that
    - Study comprises `r parms[["ncase"]]` cases and `r parms[["kctl"]]` controls per case.
    - Proportion $p_n$ of exposed among controls is `r parms[["pn"]]*100`%.
    - True odds-ratio of being exposed is `r parms[["or"]]`, so that $P(exposed|case) = OR \times p_n =$ `r parms[["or"]] * parms[["pn"]]*100`%.
    - Exposed cases have a shorter spacing between doses relative to controls and unexposed cases (`r parms[["mean_x_exp"]]` vs `r parms[["mean_x_unexp"]]` days).
    
```{r make_mcc}

```


```{r run sim}

```

```{r check}

```
- We can look at the contingency table (control/case by unexposed/exposed)
```{r}
m
```
- Raw OR is `r round(or, 2)`
- And the delay distribution is shifted for exposed cases
```{r, fig.width=5, fig.height=5}
p0
```

- Model parameterization is either
   - One categorical variable of exposure $E$ that combines $V$ and quantiles of $X$: "Unexposed", "Exposed and 1st quantile of x", "Exposed and 2nd... etc". So that $E$ has (1 + $k$ quantiles) categories.
   $$logitP(Y=1) \sim \beta_0 + \beta_1 E$$
   - One binary variable of exposure + one continuous variable for spacing + interaction term. Or $$logitP(Y=1) \sim \beta_0 + \beta_1 V + \beta_2 X + \beta_3 (V \times X)$$

## Categorized $X$
```{r quantiles}

```
- odds ratio by category
```{r}
res
```
## Continuous $X$
- partial-effect plot 
```{r spline, warning=FALSE, fig.width=3, fig.height=3}

```

